What is disputed on the web?

### 2010-01-28 papers/wicow_claimfinder/claimfinder.tex
Added mendeley bib to git. It's automatically generated so don't edit it, but others need this file in order to properly build the paper. Also reordered some sections and fixed up some references

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\and
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Tye Rattenbury\\
       \affaddr{Intel Principles and Practices}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{tye.l.rattenbury@intel.com}
}

@@

We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{hearst-hyponyms} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{textrunner} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{rte-3} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

@@

@@

>>>>

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\and
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

We have found many other patterns that can be used in this way, some of which we list in Figure~\ref{templates}. Pattern searching methods like these have been used by other authors previously, most notably by Marti Hearst~\cite{Hearst1992} who looked for patterns such as ``{\it animals} such as {\it cats}'' to identify hyponyms.

@@

There has been significant work on detecting contradictions. Condoravdi et al~\cite{Condoravdi2003} argue that contradiction detection is one of the key tasks in language understanding. de Marneffe et al~\cite{deMarneffe2008} present a taxonomy of the different ways that claims can contradict each other and describe a system that combines many techniques to detect different kinds of contradiction. AuContraire~\cite{Ritter2008} uses TextRunner~\cite{Banko2007} to infer subject-verb-object relationships, looks for cases where a verb maps the same subject to multiple objects, and uses semantic knowledge to determine when this implies that there is a contradiction. Harabagiu et al~\cite{Harabagiu2006} look for contradictions where one claim is a negated paraphrase of another. The RTE-3 Recognizing Textual Entailment challenge~\cite{Giampiccolo2007} included an optional contradiction detection task, allowing different groups building contradiction detection algorithms to compare their results.

@@

Not every chunk of text identified by one of our patterns is a well-formed disputed claim. Consider for example the text chunks in Figure~\ref{filtered}.

We use a simple natural language parser to filter the chunks of text that match our patterns.

@@

\subsection{Context}

\x{Importance of dates}
\x{Work meaning depending on surrounding text}
\x{We do not yet do anything useful with context, but we believe it is important and intend to use it}

@@

\todo{Lots of pretty graphs showing what our data is like.}

### 2010-01-28 papers/wicow_claimfinder/relatedwork.tex
No changes. Commiting to allow merge.
Fleshing out the paper. We now have some rough text for every section except the bits on what one can use this data for, and an exploration of the date itself
Added mendeley bib to git. It's automatically generated so don't edit it, but others need this file in order to properly build the paper. Also reordered some sections and fixed up some references

\subsection{What is credible?}

@@

The automatic analysis of text falls into the field of natural language processing (NLP) 
and the problems and methods described here draw from a variety of sub-areas within the NLP literature. 
The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
candidate claims  is inspired by \cite{hearst92} and is an instance of template inference (aka pattern matching) 
that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
\cite{etzioni05} for information extraction). {\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.

@@

This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
text can be inferred from the other text (add references). Disputed claims can be seen as 
contradictions, contradictions occur when information found in two different texts is 
incompatible\cite{harabagiu}. Here {\bf XX}.

%\subsection{Contradiction Detection}

%\subsection{Sentiment Analysis}

\subsection{Crowdsourcing disputed claims}

\x{Dispute Finder. Wikipedia. WikiTrust}

\subsection{Curated Databases of Disputed Claims}

\x{Dispute Finder.}

>>>>

@@

The automatic analysis of text falls into the field of natural language processing (NLP) 
and the problems and methods described here draw from a variety of sub-areas within the NLP literature. 
The method described in Section~\ref{sec:XX} that uses a set of XX extraction patterns to generate 
candidate claims  is inspired by \cite{Hearst92} and is an instance of template inference (aka pattern matching) 
that has been used extensively for several NLP task (for example \cite{Riloff93}, \cite{Jones99} and 
\cite{etzioni05} for information extraction). {\bf XX DESCRIBE SIMILARITIES AND DIFFENRENCES}.

@@

This work is also closely related to the NLP areas of opinion mining and/or sentiment analysis, 
textual entailment and contradiction detection. Sentiment analysis aims to determine the attitude 
(usually positive, negative and neutral) of a writer with respect to some topic\cite{pangLee}. 
Textual entailment is the task of deciding, given two text fragments, whether the meaning of one 
text can be inferred from the other text (add references). Disputed claims can be seen as 
contradictions, contradictions occur when information found in two different texts is 
incompatible\cite{Harabagiu2006}. Here {\bf XX}.
